An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-11 paper.tex

Once the data is cleaned there are two methods that allow the user to extract
the cleaned data: either extract sections of the data bounded by the events
recorded in the \verb|record-xxx.txt| file or save the cleaned data to disk.
These operations are available as a command line application and as an
application programming interface (API) in Python. An example of the
\verb|DFlowData| API in use is provided in Listing~\ref{lis:dflowdata}.
%
\begin{listing}
  \begin{minted}[gobble=4]{python}
    >>> from gaitanalysis.motek import DFlowData
    >>> data = DFlowData('mocap-020.txt', 'record-020.txt',
    ...                  'meta-020.yml')
    >>> mass = data.meta['subject']['mass']
    >>> data.clean_data()
    >>> event_df = data.extract_processed_data(
    ...     event='Longitudinal Perturbation')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could load a
    trial into memory, extract the subject's mass from the meta data, run the
    data cleaning process, and finally extract a Pandas \verb|DataFrame|
    containing all of the time histories for a specific event in the trial.}
  \label{lis:dflowdata}
\end{listing}

The \verb|GaitData| class is then used to compute gait events (toe off and heel
strike times), basic 2D kinematics and inverse dynamics, and to store the data
into a Pandas \verb|Panel| with each gait cycle on the item axis at a specified
sampling rate. This object can also be serialized to disk in HDF5 format. An
example of using the Python API is shown in Listing~\ref{lis:gaitdata}.
%
\begin{listing}
  \begin{minted}[gobble=4]{python}
    >>> from gaitanalysis.gait import GaitData
    >>> gdata = GaitData(event_df)
    >>> gdata.inverse_dynamics_2d(left_markers, right_markers,
    ...                           left_loads, right_loads, mass, 6.0)
    >>> gdata.grf_landmarks('Right Fy', 'Left Fy', threshhold=20.0)
    >>> gdata.split_at('right')
    >>> gdata.plot_gait_cycles('Left Hip Joint Torque', mean=True)
    >>> gdata.save('gait-data.h5')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could use the
    \verb|GaitData| class to load in the result of \verb|DFlowData| and compute
    the inverse dynamics (joint angles and torques), identify the gait events
    (e.g. heel strikes), split the data with respect to the gait events into a
    Pandas \verb|Panel|, plot the mean and standard deviation of one time
    history with respect to the gait cycles, and save the data to disk.}
  \label{lis:gaitdata}
\end{listing}

>>>>

Once the data is cleaned there are two methods that allow the user to extract
the cleaned data: either extract sections of the data bounded by the events
recorded in the \verb|record-xxx.txt| file or save the cleaned data to disk.
These operations are available as a command line application and as an
application programming interface (API) in Python. An example of the
\verb|DFlowData| API in use is provided in Listing~\ref{lis:dflowdata}.
%
\begin{listing}
  \begin{minted}{pycon}
>>> from gaitanalysis.motek import DFlowData
>>> data = DFlowData('mocap-020.txt', 'record-020.txt',
...                  'meta-020.yml')
>>> mass = data.meta['subject']['mass']
>>> data.clean_data()
>>> event_df = data.extract_processed_data(
...     event='Longitudinal Perturbation')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could load a
    trial into memory, extract the subject's mass from the meta data, run the
    data cleaning process, and finally extract a Pandas \verb|DataFrame|
    containing all of the time histories for a specific event in the trial.}
  \label{lis:dflowdata}
\end{listing}

The \verb|GaitData| class is then used to compute gait events (toe off and heel
strike times), basic 2D kinematics and inverse dynamics, and to store the data
into a Pandas \verb|Panel| with each gait cycle on the item axis at a specified
sampling rate. This object can also be serialized to disk in HDF5 format. An
example of using the Python API is shown in Listing~\ref{lis:gaitdata}.
%
\begin{listing}
  \begin{minted}{pycon}
>>> from gaitanalysis.gait import GaitData
>>> gdata = GaitData(event_df)
>>> gdata.inverse_dynamics_2d(left_markers, right_markers,
...                           left_loads, right_loads, mass, 6.0)
>>> gdata.grf_landmarks('Right Fy', 'Left Fy', threshhold=20.0)
>>> gdata.split_at('right')
>>> gdata.plot_gait_cycles('Left Hip Joint Torque', mean=True)
>>> gdata.save('gait-data.h5')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could use the
    \verb|GaitData| class to load in the result of \verb|DFlowData| and compute
    the inverse dynamics (joint angles and torques), identify the gait events
    (e.g. heel strikes), split the data with respect to the gait events into a
    Pandas \verb|Panel|, plot the mean and standard deviation of one time
    history with respect to the gait cycles, and save the data to disk.}
  \label{lis:gaitdata}
\end{listing}
